Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-13 qpip0.tex

\hannote{In this section, we modify the construction of \cite{FOCS:Mahadev18a} to show that a $\QPIP_1$ protocol for $\SampBQP$ implies a $\QPIP_0$ for $\SampBQP$.}

We then extend our scheme for $\QPIP_0$ using results from \cite{FOCS:Mahadev18a}.

Here we combine \cref{QPIP1thm} with results from \cite{FOCS:Mahadev18a} to create a delegation protocol for $\SampBQP$ for fully classical clients. Combining them will cost polynomially rounds, so we use results from \cite{parallelrep} that allows parallel repetition to construct a constant-round protocol.

@@

\begin{theorem}
    \label{Mahadev_QPIP0_Protocol_Interface}
	Under the assumption that the learning with errors problem with superpolynomial noise ratio is computationally intractable for an efficient quantum machine, there exists a $\QPIP_0$ protocol $(\bbV, \bbP)$ with the following properties:
	\begin{itemize}
	    \item The protocol runs either a ``Hadamard round" or a ``test round".
	    \item With a test round, the verifier outputs nothing other than accept/reject
	    \item With a Hadamard round, for prover $\bbP'$, the verifier also obtains a sample from $D_{\bbP', h}$. We define $D^C_{\bbP', h}$ as that distribution conditioned on acceptance.
	    \item (completeness) $\forall\rho\in\mathcal{B}^{\otimes n}$ and $h\in\set{0,1}^n$, there is a prover with negligible reject probability. Furthermore, $D^C_{\bbP, h}$ has negligible total variation distance to $D_{\rho, h}$
	    \item (soundness) Fix $\bbP'$ and $h$. Let $p_{h, H}$ be its rejection probability under a Hadamard round, and $p_{h, T}$ be its rejection probability under a test round. Then $\exists\tilde\bbP$ s.t. $\norm{D^C_{\bbP', h} - D_{\tilde\bbP, h}}\leq p_{h,H} + \sqrt{p_{h, T}}+\mu$ for some negligible $\mu$, and $\exists\rho$ s.t. $D_{\tilde\bbP, h}$ is computationally indistinguishable from $D_{\rho, h}$.
		\item This is a 4-round protocol. The prover does not know whether it is a test or Hadamard round until the end of 3rd round.
		\begin{enumerate}
			\item The verifier generates $(k, td)$, ``key" and ``trapdoor". It sends the key to the prover.
			\item The prover computes a classical ``commitment" $y$ and sends it to the verifier.
			\item The verifier sends $c\in\set{0, 1}$, where $c=0$ corresponds to test round and $c=1$ corresponds to Hadamard round.
			\item The prover computes and sends a classical string $a$
		\end{enumerate}
	\end{itemize}
\end{theorem}

\hannote{import urmila protocol description.. up}
Here, we recall the Mahadev's protocol \cite{FOCS:Mahadev18a}. We only give a high-level description of the protocol and properties of it and omit the details since they are not needed to show our result.

The protocol is run between a quantum prover $\pro$ and a classical verifier $\ver$ on a common input $x$. The aim of the protocol is to enable a verifier to classically verify $x\in \lang$ for a BQP language $\lang$ with the help of interactions with a quantum prover.
The protocol is a 4-round protocol where the first message is sent from $\ver$ to $\pro$. 
We denote the $i$-th message generation algorithm by $\ver_i$ for $i\in\{1,3\}$ or $\pro_i$ for $i\in \{2,4\}$ and denote the verifier's final decision algorithm by $\ver_\out$.
Then a high-level description of the protocol is given below.
\begin{description}
\item[$\ver_1$:] On input the security parameter $1^\secpar$ and $x$, it generates a pair $(\key,\td)$ of a``key" and ``trapdoor", sends $\key$ to $\pro$, and keeps $\td$ as its internal state.
\item[$\pro_2$:] On input $x$ and $\key$, it generates a classical ``commitment" $\comy$ along with a quantum state $\ket{\st_\pro}$, sends $\comy$ to $\pro$, and keeps $\ket{\st_\pro}$ as its internal state.
\item[$\ver_3$:] It randomly picks $c\sample \bit$ and sends $c$ to $\pro$.\footnote{The third message is just a public-coin, and does not depend on the transcript so far or $x$.}
Following the terminology in \cite{FOCS:Mahadev18a}, we call the case of $c=0$ the ``test round" and the case of $c=1$ the ``Hadamard round".
\item[$\pro_4$:] On input $\ket{\st_\pro}$ and $c$, it generates a classical string $\ans$ and sends $\ans$ to $\pro$.
\item[$\ver_\out$:] On input $\key$, $\td$, $y$, $c$, and $\ans$, it returns $\top$ indicating acceptance or $\bot$ indicating rejection.
In case $c=0$, the verification can be done publicly, that is, $\ver_\out$ need not take $\td$ as input.
\end{description}

For the protocol, we have the following properties:\\
\noindent\textbf{Completeness:}
For all $x\in \lang$, we have $\Pr[\langle \pro,\ver \rangle(x)]=\bot]= \negl(\secpar)$.\\
\noindent\textbf{Soundness:}
If the LWE problem is hard for quantum polynomial-time algorithms, then for any $x\notin \lang$ and a quantum polynomial-time cheating prover $\pro^*$, we have  $\Pr[\langle \pro^*,\ver \rangle(x)]=\bot]\leq 3/4$.

We need a slightly different form of soundness implicitly shown in \cite{FOCS:Mahadev18a}, which roughly says that if a cheating prover can pass the ``test round" (i.e., the case of $c=0$) with overwhelming probability, then it can pass the ``Hadamard round" (i.e., the case of $c=1$) only with a negligible probability. 
\begin{lemma}[implicit in \cite{FOCS:Mahadev18a}]\label{lem:Mah_soundness}
If the LWE problem is hard for quantum polynomial-time algorithms, then for any $x\notin \lang$ and a quantum polynomial-time cheating prover $\pro^*$ such that  $\Pr[\langle \pro^*,\ver \rangle(x)]=\bot\mid c=0]=\negl(\secpar)$, we have $\Pr[\langle \pro^*,\ver \rangle(x)]=\top\mid c=1]=\negl(\secpar)$.
\end{lemma}

We will also use the following simple lemma:
\begin{lemma}\label{fact:perfectly_pass_test}
There exists an efficient prover that passes the test round with probability $1$ (but passes the Hadamard round with probability $0$) even if $x\notin \lang$. 
\end{lemma}

@@

\begin{lem}[\hannote{ref}]~\label{lem:trivial-4-round-strategy}
    For any input, there exist a prover strategy $(U_{trivial,0},U_{trivial})$ for Protocol~\ref{proto:urmila4} that is accepted with probability $1-\negl{n}$ in the testing round and \hannote{binding?}.
\end{lem}

\begin{definition}[quantum computationally indistinguishable]
\hannote{move later}
Let  $D_1$ and $D_2$ be distributions over $n$-bit string.  We say $D_1$ and $D_2$  are $\eps$-Q-computationally indistinguishable if for all quantum circuit $A$ of size $\poly(n)$, $$\L\|\Pr[A({D_1})=1]-\Pr[A({D_2})=1]  \R\| \leq \eps,$$  where $A(D_1)$ means $A$ takes \emph{one} sample from $D_1$ as part of its input. We also denote "$D_1$ and $D_2$  are $\eps$-Q-computationally indistinguishable" as 
$$ \norm{D_1 - D_2}_q \leq \eps.$$
And "$D_1$ and $D_2$  are not $\eps$-Q-computationally indistinguishable" as 
$$ \norm{D_1 - D_2}_q > \eps.$$
\end{definition}
%Let $O^{D_1}$ and $O^{D_2}$ be oracles giving samples from $D_1$ and $D_2$.

\begin{rmk}
We extend the definition of computational distance to a subnormalized distribution  $D$  by assuming $A(D)=0$ when $A$ fail to draw a sample from $D$.
\end{rmk}

\begin{rmk}\label{rmk:trace-to-comp}
If $\norm{D_1-D_2}_1\leq \eps$, $D_1$ and $D_2$ are $\eps$-Q-computationally indistinguishable.
\end{rmk}

\begin{lem}[triangle inequality for computational distance] \label{lem:computational-triangle0}
    Let $D_1$, $D_2$, and $D_3$ be three distributions such that 
    \begin{align}
        \norm{D_1 -D_2}_q &\leq \eps \\ 
        \norm{D_2 -D_3}_q &\leq \eps'. 
    \end{align}
    We have 
    \begin{align}
        \norm{D_1 -D_3}_q &\leq \eps+\eps'
    \end{align}
\end{lem}
\begin{proof}
For all quantum circuits $A$ with size $\poly(n)$, we have 
\begin{align}
    \norm{\Pr[A({D_1})=1]-\Pr[A({D_2})=1]} \leq& \eps \\
    \norm{\Pr[A({D_2})=1]-\Pr[A({D_3})=1]} \leq& \eps',  
\end{align}
so 
\begin{align}
    &\norm{\Pr[A({D_1})=1]-\Pr[A({D_3})=1]} \nn \\
    =& \norm{\Pr[A({D_1})=1]-\Pr[A({D_2})=1]+\Pr[A({D_2})=1]-\Pr[A({D_3})=1]} \nn \\
    \leq&  \norm{\Pr[A({D_1})=1]-\Pr[A({D_2})=1]} +\norm{\Pr[A({D_2})=1]-\Pr[A({D_3})=1]} \nn \\
    =& \eps +\eps' \nn
\end{align}

\begin{lem}[another triangle inequality for computational distance \hannote{unused}]\label{lem:computational-triangle}
Let $D_1$, $D_2$ be two distributions such that $D_1=D_3+D_4$ and $D_2=D_5+D_6$, where $D_3$, $D_4$, $D_5$, and $D_6$ are subnormalized distributions.

If 
\begin{align}
    &\norm{D_1 - D_2}_q \leq \eps   \\ 
    &\norm{D_4 - D_6}_q \leq \eps',  
\end{align}
then 
\begin{align}
   \norm{ D_3 - D_5}_q \leq \eps+\eps' 
\end{align}
\end{lem}
% \begin{align}
%     D_1 &\approx_{q,\eps} D_2 \\
%     D_4 &\approx_{q,\eps'} D_6, 
% \end{align}
% then 
% \begin{align}
%     D_3 \approx_{q,\eps+\eps'} D_5
% \end{align}
\begin{proof}
% Since
% $$\norm{D_4 - D_6}_q \leq \eps',$$
% there exist

We prove by contradiction. Suppose that
$$\norm{ D_3 - D_5}_q > \eps+\eps',$$
then there exist a quantum circuit $A$ of size $poly(n)$ such that 
$$\L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1]  \R\| > \eps+\eps'.$$
Since $$\norm{D_4 - D_6}_q \leq \eps'$$, we know that 
$$\L\|\Pr[A({D_4})=1]-\Pr[A({D_6})=1]  \R\| \leq \eps'.$$
Since $D_1=D_3+D_4$ and $D_2=D_5+D_6$, we have that
$$ \Pr[A({D_1})=1]= \Pr[A({D_3})=1]+ \Pr[A({D_4})=1]$$ 
$$ \Pr[A({D_2})=1]= \Pr[A({D_5})=1]+ \Pr[A({D_6})=1].$$ 
So 
\begin{align}
    &\L\|\Pr[A({D_1})=1]-\Pr[A({D_2})=1]  \R\| \nn \\
    =&   \L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1] +\Pr[A({D_4})=1]-\Pr[A({D_6})=1]  \R\| \nn \\
    \geq  &\L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1]  \R\| - \L\|\Pr[A({D_6})=1]-\Pr[A({D_4})=1]  \R\|  \nn \\
     > &\eps 
\end{align}
This contradicts with the assumption that $\norm{D_1 - D_2}_q \leq \eps $.
\end{proof}

\hannote{comp. indistinguish for subnormalized state?}
\hannote{triangle inequality}

\begin{lemma}\label{lem:urmila-binding}[binding property of  Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
If a prover's strategy in Protocol~\ref{proto:urmila4}\hannote{need clarification} results in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that for all $h$, the prover will produce a $z$ on the Hadamard round that is $\negl(n)$-Q-computationally indistinguishable from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer. 
\end{lemma}

@@

We combine the commitment Protocol, Protocol~\ref{proto:urmila4}, and the $\QPIP_1$ Protocol, Protocol~\ref{ProtoQPIP1}, to get a naive $\QPIP_0$ Protocol for $\SampBQP$ that has no soundness guarantee.

@@

 	Ingrediants:
 	\begin{itemize}
 		\item Let $C$ be a quantum circuit consisting of only Hadamard and Toffoli gates, which on input $x$ samples from some $C_x$ such that $\norm{C_x-D_x}\leq\varepsilon$.
 		\item Let $C'$ be $C$ padded with $\frac{T}{\varepsilon}$ identity gates at the end.
 		\item Let $H_{C'(x)}$ be the local Hamiltonian instance associated with the computation of $C'(x)$.
		\item Let $\ket{\psi_{C'(x)}}$ be the ground state of $H_{C'(x)}$.
%  		\item Let $\cVGS$ be the way to verify said ground state as defined in \Cref{AlgGroundStateCheck}. \Ethan{TODO wording needs fix...? How?}
 	\end{itemize}

@@

	\item \label{step:urmila-in-naive} The verifier and prover run Protocol~\ref{proto:urmila4}, with the following parameters: $h$ is chosen from previous step, $n_{commit}=M \times$ (number of qubits in $\ket{\psi_{C'(x)}}$), where $n_{commit}$ is the $n$ for Protocol~\ref{proto:urmila4}, and the honest prover choose $M$ copies of $\ket{\psi_{C'(x)}}$ as $\rho$. We also allow a cheating prover to send $\bot$ in the fourth round of Protocol~\ref{proto:urmila4} if $c=1$ to abort the process.\footnote{This is useless for the cheating prover but useful for proving one of our theorems.} If the verifier receives $\bot$ in the fourth round, he outputs $(\Rej,\bot)$ and terminates this protocol.

@@

@@

\subsection{$\QPIP_0$ protocol for $\SampBQP$}
%Parallel Repetition of the Measurement Subprotocol

@@

\begin{protocol}{$\QPIP_0$ for $\SampBQP$}
\label{proto:QPIP0samp}
Inputs: 
 Both verifier and prover start with the description of number of qubits $n$,  input string $x$ to the $\SampBQP$ Instance, and a soundness parameter $\varepsilon$.

@@

%Let $S_m$ be sets of $\{c\}$ such that only one of the $c_i=1$.
\begin{lemma}[partition lemma2]\label{lem:partition2}
Let $(U_0,U)$ be a prover's strategy in Protocol~\ref{proto:QPIP0samp}, where $U_0$ is the how the prover generates answer in the second round, and $U$ is how the prover generates answer in the fourth round. Denote the string $0^{i-1}10^{m-i} \in \zo^m $ as $e_i$.  Let $\gamma_0 \in[0,1]$, and $T\in \mathbb{N}$ such that $\gamma_0=1/\poly(n)$ and $T=\poly(n)$.

 For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exist two efficient quantum circuit $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ such that for all (possibly sub-normalized)  quantum state $\ket{\psi}_{\regX,\regZ}$,  \hannote{$\psi$ should not be pure state?} \hannote{actually need to fix a $pk$ for everything here.}

@@

  Note that $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ has failure probabilities, and this is reflected by the fact that $\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}$ and $\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}$ are  sub-normalized. $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ depend on $(U_0,U)$.

@@

\item \hannote{added by me..not needed?}

$$\vev{\psi_{0,i,\gamma}|\psi_{1,i,\gamma}} = \negl(n)$$

@@

$$z_i\defeq \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$
where $\ket{e_i,\psi}=\ket{e_i}_\regC\ket{\psi}_{\regX,\regZ}$ and $U$ is the unitary the prover applies on the last round. \hannote{need to average $pk$ here.}

@@

===

%Prove that $z_{good}$ is binding.
We now proceeds to prove that $z_{good}$ is binding. I.e. there exist a subnormalized $n$-qubit quantum state $\rho_{good}$ such that $z_{good}$ is $\eps$-Q-computationally indistinguishable to $M_{XZ}(\rho_{good},h)$.

\hannote{$M_{XZ}(\rho_{good},h)=\sum_z \proj{z} \tr\L(\rho \sigma_{h,z} \R)?$}.
\hannote{add notation for pauli matrix $\sigma_h$.}

\hannote{need to simulate one copy?}

@@

Therefore by Lemma~\ref{lem:computational-triangle0}, we have  
\begin{align}
     \norm{(d,z)-(d,z_{ideal})}_q \leq O(\eps)
\end{align}
\hannote{the composition of z ideal and triangle ineq is sketchy lol.}

@@

===========

\hannote{below are unused old fragments}

========= old

By Lemma~\ref{lem:trivial-4-round-strategy} and property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}, the above strategy is accepted with probability $1-\negl(n)$. Therefore by Lemma~\ref{lem:urmila-binding}, there exist a $\rho_{composite}$ such that

\begin{align}
    \norm{z_{composite} - M_{XZ}(\rho_{composite},h) }_q \leq \negl(n) 
\end{align}

By Lemma~\ref{lem:trivial-4-round-strategy} and Lemma~\ref{lem:urmila-binding}, there exist a $\rho_{trivial}$ such that

\begin{align}
    \norm{z_{trivial} - M_{XZ}(\rho_{trivial},h) }_q \leq \negl(n), 
\end{align}
where $z_{trivial}$ is the random variable one get by running the strategy of Lemma~\ref{lem:trivial-4-round-strategy}, normalized by the probability that the trivial strategy is chosen in the composite strategy. $\rho_{trivial}$ is normalized by the same probability.

Note that when $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$ succeeded, the corresponding output would be $z_{good}$. Therefore $z_{composite}=z_{good}+z_{trivial}$, and by Lemma~\ref{lem:computational-triangle},

\begin{align} \label{eq:z-good-rho}
    \norm{z_{good} - M_{XZ}(\rho_{good},h) }_q \leq \negl(n), 
\end{align}
where $\rho_{good} \defeq \rho_{composite}-\rho_{trivial}$.

Recall that by Eq~\ref{eq:z-z-good} we have
\begin{align} \label{eq:z-z-good2}
    \norm{z-z_{good}}_1 \leq \eps
\end{align}
if we pick $m,T,\gamma_0=???$ \hannote{tune eps}

Also note that by theorem~\ref{QPIP1thm}, 
\begin{align} \label{eq:rho-c}
    \norm{M_{XZ}(\rho_{good},h) -p_{good} C(x)}_1 \leq \eps, 
\end{align}
where $p_{good} = \tr \rho_{good}$.

Putting together Equation~\ref{eq:z-z-good2} \ref{eq:z-good-rho} \ref{eq:rho-c},  Remark~\ref{rmk:trace-to-comp}, and Lemma~\ref{lem:computational-triangle0}, we have  
\begin{align}
    \norm{z- p_{good}C(x)}_q \leq 2\eps +\negl{n}
\end{align}

==== old ===

For every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp}, consider the following composite strategy of the prover for Protocol~\ref{proto:urmila4}: on the first round the verifier pick $h$ from distribution specified by ???? of Protocol~\ref{ProtoQPIP1}. On the second round, the prover start with picking a uniformaly random $i\in [m]$. The prover then tries to run $U_0$ by taking the verifier's input as $i$-th copy of protocol~\ref{proto:QPIP0samp} and simulating other $m-1$ copies by himself. The prover then \hannote{picks a uniformly random $\gamma$ ?}  tries to generate $\ket{\psi_{1^{i-1}1,\gamma}}$ by applying $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$. If the prover fails to generate $\ket{\psi_{1^{i-1}1,\gamma}}$, he throws out everything and run $U_{trivial,0}$ described  in  Lemma~\ref{lem:trivial-4-round-strategy} instead. This is possible because all the inputs are classical. On the fourth round, if the prover had generated $\ket{\psi_{1^{i-1}1,\gamma}}$, he reply with the $i$-th register of $\ext_i\left(\frac{\ket{e_j}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)$, where $\ext_i$ is specified in property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}. otherwise he continues to run the strategy of Lemma~\ref{lem:trivial-4-round-strategy}. We denote the random variable the verifier would get on the testing round as $z_{construct}$.

===

 [[Partition lemma ->  Parallel repetition]], except for probability $\eps$\hannote{$\frac{1}{poly}$?}, either the verifier reject at step~\ref{step:multi-testing} or $z$ is $\negl(n)$-computationally indistinguishable to $M_{XZ}(\rho,h)$ by Lemma~\ref{lem:urmila-binding}.

 By theorem~\ref{QPIP1thm}, $M_{XZ}(\rho,h)$  $\eps$-close to $C(x)$. Therefore, $M_{XZ}(\rho,h)$  and  $C(x)$ $z$ are $\eps$-Q-computationally indistinguishable, and thus $z$ and $C(x)$ are  $2\eps$-Q-computationally indistinguishable.

===========

\hannote{import 3.5. didn't import the proof, too long.}

First, We present a slight adaption of Lemma 3.5 of \cite{parallelrep}  that partitions the prover's internal state. We omit the proof here.

%$\frac{\gamma_0}{T}=1/\poly(\secpar)$
\begin{lemma}[partition lemma]\label{lem:partition}
Let $(U_0,U)$ be a prover's strategy in Protocol~\ref{proto:QPIP0samp}, where $U_0$ is the how the prover generates answer in the second round, and $U$ is how the prover generates answer in the fourth round. Let $S_m$ be sets of $\{c\}$ such that only one of the $c_i=1$. Let $\gamma_0 \in[0,1]$, and $T\in \mathbb{N}$ such that $\gamma_0=1/\poly(n)$ and $T=\poly(n)$.

 For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exists an $\poly(n)$-sized quantum circuit $G_{i,\gamma}$ such that for all (possibly sub-normalized) \hannote{$n$-qubit?} quantum state $\ket{\psi}_{\regX,\regZ}$,  
\begin{align*}
    G_{i,\gamma} \ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0^t}_{ph}\ket{0}_{th}\ket{0}_{in} = \\ \ket{0^m}_{\regC}\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}\ket{0^t01}_{ph,th,in}+  \ket{0^m}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}\ket{0^t11}_{ph,th,in} + \ket{\psi'_{err}}
\end{align*}
 where $t$ is the number of qubits in the register $ph$, $\ket{\psi_0}_{\regX,\regZ}$, $\ket{\psi_1}_{\regX,\regZ}$, and $\ket{\psi_{err}}_{\regX,\regZ}$ are sub-normalized states that may depend on $\gamma$.

Furthermore, the following properties are satisfied for all $i\in[m]$.
%
\begin{enumerate}
    \item \label{partition-property-1}  Define $\ket{\psi_{err}}_{\regX,\regZ}\defeq \ket{\psi}_{\regX,\regZ} - \ket{\psi_{0}}_{\regX,\regZ}- \ket{\psi_{1}}_{\regX,\regZ}$.\hannote{?} We have  $$E_{\gamma}[\|\ket{\psi_{err}}_{\regX,\regZ}\|^2]\leq \frac{6}{T}+\negl(n)$$. 
    $$\|\ket{\psi}_{\regX,\regZ}\|^2 -E_{\gamma}\L[\|\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}\|^2 +\|\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}\|^2\R]\leq \frac{6}{T}+\negl(n),$$

    where the averaged is over uniformly sampled $\gamma$.
\item For any fixed $\gamma$, $\Pr[M_{ph,th,in}\circ \ket{\psi'_{err}} \in \{0^t01,0^t11\}] =0$. %where $M_{ph,th,in}$ is the computational-basis measurement in the register $(ph,th,in)$. %and $t$ is the number of qubits in $ph$.   
This implies that if we apply the measurement $M_{ph,th,in}$ on $\frac{G_{i,\gamma} \ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0^t}_{ph}\ket{0}_{th}\ket{0}_{in}}{\|\ket{\psi}_{\regX,\regZ}\|}$, then the outcome is $0^tb1$ with probability $\|\ket{\psi_b}_{\regX,\regZ}\|^2$ and the resulting state in the register $(\regX,\regZ)$  is $\frac{\ket{\psi_b}_{\regX,\regZ}}{\|\ket{\psi_b}_{\regX,\regZ}\|}$ ignoring a global phase factor.

    % \item For any fixed $\gamma$, $E_{b\in \{0,1\}} [\|\ket{\psi_b}_{\regX,\regZ}\|^2]\leq \frac{1}{2}\|\ket{\psi}_{\regX,\regZ}\|^2$. \hannote{redundant?}

%     \begin{align*}
% \Pr\left[M_{\regX_i}\circ U\frac{\ket{\{c\}}_{\regC}\ket{\psi_0}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}\in \Acc_{k_i,y_i}\right]\leq (m-1)\gamma+\negl(\secpar).
% \end{align*}

>>>>

%\hannote{In this section, we modify the construction of \cite{FOCS:Mahadev18a} to show that a $\QPIP_1$ protocol for $\SampBQP$ implies a $\QPIP_0$ for $\SampBQP$.}

% We then extend our scheme for $\QPIP_0$ using results from \cite{FOCS:Mahadev18a}.

In this section, we combine \cref{QPIP1thm} with results from \cite{FOCS:Mahadev18a} to create a delegation protocol for $\SampBQP$ for fully classical clients. To boost the soundness, we need  polynomial rounds, so we use results from \cite{parallelrep} to run polynomially many copies in parallel and get a constant-round protocol.

@@

@@

\begin{lem}[\hannote{ref}]~\label{lem:trivial-4-round-strategy}
    For any input, there exist a prover strategy $(U_{trivial,0},U_{trivial})$ for Protocol~\ref{proto:urmila4} that is accepted with probability $1-\negl{n}$ in the testing.
\end{lem}

% \begin{lem}[another triangle inequality for computational distance \hannote{unused}]\label{lem:computational-triangle}
% Let $D_1$, $D_2$ be two distributions such that $D_1=D_3+D_4$ and $D_2=D_5+D_6$, where $D_3$, $D_4$, $D_5$, and $D_6$ are subnormalized distributions.

% If 
% \begin{align}
%     &\norm{D_1 - D_2}_q \leq \eps   \\ 
%     &\norm{D_4 - D_6}_q \leq \eps',  
% \end{align}
% then 
% \begin{align}
%   \norm{ D_3 - D_5}_q \leq \eps+\eps' 
% \end{align}
% \end{lem}
% % \begin{align}
% %     D_1 &\approx_{q,\eps} D_2 \\
% %     D_4 &\approx_{q,\eps'} D_6, 
% % \end{align}
% % then 
% % \begin{align}
% %     D_3 \approx_{q,\eps+\eps'} D_5
% % \end{align}
% \begin{proof}
% % Since
% % $$\norm{D_4 - D_6}_q \leq \eps',$$
% % there exist

% We prove by contradiction. Suppose that
% $$\norm{ D_3 - D_5}_q > \eps+\eps',$$
% then there exist a quantum circuit $A$ of size $poly(n)$ such that 
% $$\L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1]  \R\| > \eps+\eps'.$$
% Since $$\norm{D_4 - D_6}_q \leq \eps'$$, we know that 
% $$\L\|\Pr[A({D_4})=1]-\Pr[A({D_6})=1]  \R\| \leq \eps'.$$
% Since $D_1=D_3+D_4$ and $D_2=D_5+D_6$, we have that
% $$ \Pr[A({D_1})=1]= \Pr[A({D_3})=1]+ \Pr[A({D_4})=1]$$ 
% $$ \Pr[A({D_2})=1]= \Pr[A({D_5})=1]+ \Pr[A({D_6})=1].$$ 
% So 
% \begin{align}
%     &\L\|\Pr[A({D_1})=1]-\Pr[A({D_2})=1]  \R\| \nn \\
%     =&   \L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1] +\Pr[A({D_4})=1]-\Pr[A({D_6})=1]  \R\| \nn \\
%     \geq  &\L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1]  \R\| - \L\|\Pr[A({D_6})=1]-\Pr[A({D_4})=1]  \R\|  \nn \\
%      > &\eps 
% \end{align}
% This contradicts with the assumption that $\norm{D_1 - D_2}_q \leq \eps $.
% \end{proof}

Mahadev's 4-round protocol has the following binding property.

\begin{lemma}\label{lem:urmila-binding}[binding property of  Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
If a prover's strategy in Protocol~\ref{proto:urmila4}\hannote{need clarification} results in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that for all $h$, the prover will produce a $z$ on the Hadamard round that is $\negl(n)$-Q-computationally indistinguishable\footnote{Recall that quantum computational indistinguishability is defined in Definition~\ref{def:comp-indis}.} from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer. 
\end{lemma}

@@

By combining the commitment Protocol, Protocol~\ref{proto:urmila4}, and the $\QPIP_1$ Protocol, Protocol~\ref{ProtoQPIP1}, we get a naive $\QPIP_0$ Protocol for $\SampBQP$ that has no soundness guarantee.

@@

 	Ingrediants:
 	\begin{itemize}
 		\item Let $C$ be a quantum circuit consisting of only Hadamard and Toffoli gates, which on input $x$ samples from some $C_x$ such that $\norm{C_x-D_x}\leq\varepsilon$.
 		\item Let $T$ be the number of gates in $C$.
		\item Let $C'$ be $C$ padded with $\frac{6T}{\varepsilon}$ identity gates at the end.
 		\item Let $H_{C'(x)}$ be the local Hamiltonian instance associated with the computation of $C'(x)$.
		\item Let $\ket{\psi_{C'(x)}}$ be the ground state of $H_{C'(x)}$.
		\item Let $s=n+T+\frac{6T}{\varepsilon}$ be the number of qubits in $\ket{\psi_{C'(x)}}$
%  		\item Let $\cVGS$ be the way to verify said ground state as defined in \Cref{AlgGroundStateCheck}. \Ethan{TODO wording needs fix...? How?}
 	\end{itemize}

@@

	\item \label{step:urmila-in-naive} The verifier and prover run Protocol~\ref{proto:urmila4}, with the following parameters: $h$ is chosen from previous step, $n_{commit}=M \, s$ , where $n_{commit}$ is the $n$ for Protocol~\ref{proto:urmila4}, and the honest prover choose $M$ copies of $\ket{\psi_{C'(x)}}$ as $\rho$. We also allow a cheating prover to send $\bot$ in the fourth round of Protocol~\ref{proto:urmila4} if $c=1$ to abort the process.\footnote{This is useless for the cheating prover but useful for proving one of our theorems.} If the verifier receives $\bot$ in the fourth round, he outputs $(\Rej,\bot)$ and terminates this protocol.

@@

 Protocol~\ref{proto:qpip0_naive} has no soundness guarantee, but it has the following binding property that would be useful in proving the soundness of the actual protocol in Section~\ref{sec:qpip0}.

@@

\subsection{$\QPIP_0$ protocol for $\SampBQP$} \label{sec:qpip0}
%Parallel Repetition of the Measurement Subprotocol

@@

\begin{protocol}{$\QPIP_0$ for $\SampBQP$}
\label{proto:QPIP0samp}

\hannote{fix inputs}
Inputs: 
 Both verifier and prover start with the description of number of qubits $n$,  input string $x$ to the $\SampBQP$ Instance, and a soundness parameter $\varepsilon$.

@@

%Let $S_m$ be sets of $\{c\}$ such that only one of the $c_i=1$.
\begin{lemma}[partition lemma]\label{lem:partition2}
Let $(U_0,U)$ be a prover's strategy in Protocol~\ref{proto:QPIP0samp}, where $U_0$ is the how the prover generates answer in the second round, and $U$ is how the prover generates answer in the fourth round. Denote the string $0^{i-1}10^{m-i} \in \zo^m $ as $e_i$.  Let $\gamma_0 \in[0,1]$, and $T\in \mathbb{N}$ such that $\gamma_0=1/\poly(n)$ and $T=\poly(n)$.

 For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exist two efficient quantum circuit $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ such that for all (possibly sub-normalized)  quantum state $\ket{\psi}_{\regX,\regZ}$,

@@

  Note that $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ has failure probabilities, and this is reflected by the fact that $\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}$ and $\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}$ are  sub-normalized. $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ depend on $(U_0,U)$ and $pk,sk,y$. \hannote{check}

@@

% \item \hannote{added by me..not needed?}

% $$\vev{\psi_{0,i,\gamma}|\psi_{1,i,\gamma}} = \negl(n)$$

@@

$$z_i\defeq \E_{pk,y} \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$
where $\ket{e_i,\psi}=\ket{e_i}_\regC\ket{\psi}_{\regX,\regZ}$ and $U$ is the unitary the prover applies on the last round. \hannote{add description about  averaging $pk$ here.}

@@

We now proceeds to prove that $z_{good}$ is close to the ideal distribution.

@@

Therefore by Lemma~\ref{lem:computational-triangle0}, we have  
\begin{align}
     \norm{(d,z)-(d,z_{ideal})}_q \leq O(\eps)
\end{align}
\hannote{the composition of z ideal and triangle ineq is sketchy lol. Also need to specify different z ideal}

@@
